### 2016-09-27 readme.Rmd
fix file path and clean up examples
update README

## Usage
Installing the package:
```{r install, eval=FALSE}
library(devtools)
install_github(repo = "highlightHTML", username = "lebebr01")
```

@@

```{r function, eval=FALSE}
library(hightlightHTML)
highlightHTMLcells(input = "path/to/file", output = "path/to/saved/file", updateCSS = TRUE, tags = c("Vector of CSS code here"))
```

>>>>

## Usage
Installing the package:
```{r install, eval=FALSE}
library(devtools)
install_github('lebebr01/highlightHTML')
```

@@

```{r function, eval=FALSE}
library(hightlightHTML)
highlight_html(input = "path/to/file", output = "path/to/saved/file", updateCSS = TRUE, tags = c("Vector of CSS code here"))
```
